Supporting online material for\\ \emph{Effectiveness of UNAIDS targets and HIV vaccination across 127 countries}

### 2016-08-15 Documents/supplementary_text.tex
Long table works- but not wihin table enviornment
Working on supplement tables.

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage[final]{pdfpages}
\usepackage{float}
\usepackage{longtable}
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers,round,sort&compress]{natbib}
\usepackage{hypernat}

@@

Several sources provided information to parameterize our model at the
country level. Demographic data, including population growth rate
\cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
Bank. Longitudinal HIV incidence and prevalence estimates for the
15--49 age group, spanning from as early as 1990 to 2015, was
primarily derived from the AIDSinfo database produced by UNAIDS
\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
WHO, and the Asian Development Bank. These sources were also used to
inform the initial conditions for the model: the number of people who
have been diagnosed with HIV, who are on ART, and who have viral
suppression or have been retained on treatment for at least 12
months. Where data were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  We found sufficient data to
parametrize our mathematical modeling for 127 countries.  See
\hyperref[data_source_treatment_cascade]{Tables
  \ref*{data_source_treatment_cascade}}--\ref{data_source_regions} for
full information on data sources for each country.

\begin{table}
  \centering
  \tiny
  \input{treatment_cascade}
  \caption{Data used for the treatment cascade.}
  \label{data_source_treatment_cascade}
\end{table}

\begin{table}
  \centering
  \tiny
  % \input{prevalence}
  \caption{Data sources for prevalence.}
  \label{data_source_prevalence}
\end{table}

\begin{table}
  \centering
  \tiny
  % \input{incidence}
  \caption{Data sources for prevalence.}
  \label{data_source_incidence}
\end{table}

\begin{table}
  \centering
  \tiny
  % \input{regions}
  \caption{Countries by UNAIDS region.}
  \label{data_source_regions}
\end{table}

@@

\begin{figure}
  \centering
  \includegraphics[width = \textwidth]{../Codes/plots/transmission_rate}
  \caption{Country-specific transmission rates were calculated based
    on the relative contributions of individuals with acute infection,
    unsuppressed viral load or suppressed viral load to overall
    transmission (\autoref{model_fitting}). The estimates were
    calibrated to data on country-level incidence and/or prevalence to
    account for variation in historical incidence while accurately
    reflecting recent HIV rates.}
  \label{transmission_rate}
\end{figure}

@@

\clearpage
\input{../Codes/plots/effectiveness_all/all}

>>>>

\usepackage{amsmath}
\usepackage{geometry}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[utf8x]{inputenc}
\usepackage{microtype}
\usepackage[final]{pdfpages}
\usepackage{float}
\usepackage{longtable}
\usepackage[labelsep = period, singlelinecheck = off, labelfont = {bf}]{caption}

% Load hyperref after the other stuff above.
\usepackage[pdfborder={0 0 0}]{hyperref}
\usepackage[numbers,round,sort&compress]{natbib}
\usepackage{hypernat}

@@

Several sources provided information to parameterize our model at the
country level. Demographic data, including population growth rate
\cite{WorldBankpg}, death rate
\cite{World_Development_Indicators2013-ee}, and number of people aged
15--49 years \cite{The_World_Bank2016-fd} were obtained from the World
Bank. Longitudinal HIV incidence and prevalence estimates for the
15--49 age group, spanning from as early as 1990 to 2015, was
primarily derived from the AIDSinfo database produced by UNAIDS
\cite{Unaids2016-an}. Other sources included UNAIDS Country Progress
Reports \cite{Unaids2016-am} published from 2012 to 2016 and AIDS Data
Hub \cite{AIDSdatahub-fg}, which compiles data from UNAIDS, UNICEF,
WHO, and the Asian Development Bank. These sources were also used to
inform the initial conditions for the model: the number of people who
have been diagnosed with HIV, who are on ART, and who have viral
suppression or have been retained on treatment for at least 12
months. Where data were not available from these sources, alternative
resources such as peer-reviewed journal articles and country health
ministry reports were consulted.  We found sufficient data to
parametrize our mathematical modeling for 127 countries.  See
Supplemental data files for full information on data sources for each
country.

@@

\begin{figure}
  \centering
  \includegraphics{../Codes/plots/transmission_rate}
  \caption{Country-specific transmission rates were calculated based
    on the relative contributions of individuals with acute infection,
    unsuppressed viral load or suppressed viral load to overall
    transmission (\autoref{model_fitting}). The estimates were
    calibrated to data on country-level incidence and/or prevalence to
    account for variation in historical incidence while accurately
    reflecting recent HIV rates.}
  \label{transmission_rate}
\end{figure}

@@

\appendix
\clearpage
\section{Model results by region and country}

\input{../Codes/plots/effectiveness_all/all}

### 2016-08-15 Documents/treatment_cascade.tex
Long table works- but not wihin table enviornment
Working on supplement tables.

@@

@@

@@

2011a: Viral suppression is 12-month retention on treatment, all ages, for 2011.
2012b: Viral suppression is 12-month retention on treatment, ages 15+, for 2012.
2013a: Viral suppression is 12-month retention on treatment, all ages, for 2013.
2013b: Viral suppression is 12-month retention on treatment, ages 15+, for 2013.
2014a: Viral suppression is 12-month retention on treatment, all ages, for 2014.
2014b: Viral suppression is 12-month retention on treatment, ages 15+, for 2014.
2015a: Viral suppression is 12-month retention on treatment, all ages, for 2015.
2015b: Viral suppression is 12-month retention on treatment, ages 15+, for 2015.

>>>>

  \caption{The treatment cascade.}
  \label{data_source_treatment_cascade}
  \\[-2ex]

@@

  \endfirsthead
  \caption{(continued)}
  \\[-2ex]
  \endhead
  \endfoot
  \endlastfoot

@@

  \multicolumn{5}{l}{2011a: Viral suppression is 12-month retention on
  treatment, all ages, for 2011.} \\
  \multicolumn{5}{l}{2012b: Viral suppression is 12-month retention on
  treatment, ages 15+, for 2012.} \\
  \multicolumn{5}{l}{2013a: Viral suppression is 12-month retention on
  treatment, all ages, for 2013.} \\
  \multicolumn{5}{l}{2013b: Viral suppression is 12-month retention on
  treatment, ages 15+, for 2013.} \\
  \multicolumn{5}{l}{2014a: Viral suppression is 12-month retention on
  treatment, all ages, for 2014.} \\
  \multicolumn{5}{l}{2014b: Viral suppression is 12-month retention on
  treatment, ages 15+, for 2014.} \\
  \multicolumn{5}{l}{2015a: Viral suppression is 12-month retention on
  treatment, all ages, for 2015.} \\
  \multicolumn{5}{l}{2015b: Viral suppression is 12-month retention on
  treatment, ages 15+, for 2015.}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "supplementary_text"
%%% End:
